Experiment 2

### 2021-07-02 experiments/experiment 1/experiment 1.Rmd
Added version specification and temporary library for microxanox to experiments
re-knitted experiments

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

@@

>>>>

microxanox_release <- "0.2"

tmplib <- tempfile()
dir.create(tmplib)

### From '?remotes::install_github`:
# auth_token	
#   To install from a private repo, generate a personal access token (PAT) in
#   "https://github.com/settings/tokens" and supply to this argument. This is 
#   safer than using a password because you can easily delete a PAT without 
#   affecting any others. Defaults to the GITHUB_PAT environment variable.

remotes::install_github(
  "opetchey/microxanox",
  ref = microxanox_release,
  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
  build_vignettes = FALSE,
  force = TRUE,
  upgrade = FALSE,
  lib = tmplib
)

library(microxanox, lib.loc = tmplib)

library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

## Version of `microxinox` package used: `r packageVersion("microxanox") `

@@

```{r finalise}

### 2021-07-02 experiments/experiment 2/experiment 2.Rmd
Added version specification and temporary library for microxanox to experiments
re-knitted experiments

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
```

>>>>

microxanox_release <- "0.2"

tmplib <- tempfile()
dir.create(tmplib)

### From '?remotes::install_github`:
# auth_token	
#   To install from a private repo, generate a personal access token (PAT) in
#   "https://github.com/settings/tokens" and supply to this argument. This is 
#   safer than using a password because you can easily delete a PAT without 
#   affecting any others. Defaults to the GITHUB_PAT environment variable.

remotes::install_github(
  "opetchey/microxanox",
  ref = microxanox_release,
  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
  build_vignettes = FALSE,
  force = TRUE,
  upgrade = FALSE,
  lib = tmplib
)

library(microxanox, lib.loc = tmplib)

library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
```

## Version of `microxinox` package used: `r packageVersion("microxanox") `
